---
title: "e4_ms_models"
author: "Marissa Lee"
date: "October 19, 2014"
output: pdf_document
---

*******************

#1. Clean raw dataset (run external code)
```{r,echo=TRUE}
source('e4CodePackage_100614/e4_cleanCode.R')
#str(data)

### Read-in all the custom functions for doing stats ###
source('e4CodePackage_100614/statFxns.R')
```

*******************

+ Calculate the change in soil measurement values in the presence of M.v. (run external code)
```{r,echo=TRUE}
source('e4CodePackage_100614/e4_calcsiCode.R')
#str(datas)
```



#3. Other stats????

### Predict soil measurement using mivi biomass, compabund, and total
+ Set up model fxns (run external code.... make these into mixed effects models)  
```{r, echo=TRUE, include=FALSE}
#str(datas)
datas2<-datas
source('e4CodePackage_100614/e4_fitmodCode.R')
#ModFxn1
#ModFxn2
#ModFxn3
```
+ Set up generic fxn to pull out info from each fitted model 
+ Fit the models  
+ Organize fitted model results into tables; view the fitted model results
+ Significant model terms

Model 1. sF = (mivi * beta)  
```{r,echo=FALSE, include=FALSE}
#dim(modl1)
PvalSumm(modl1, 0.1)
```
  
Model 2. sF = (mivi * beta) + (compabund * beta2) + ((mivi * compabund) * beta3)  
```{r,echo=FALSE, include=FALSE}
#dim(modl2)
PvalSumm(modl2, 0.1)
```
  
Model 3. sF = (total * beta)  
```{r,echo=FALSE, include=FALSE}
#dim(modl3)
PvalSumm(modl3, 0.1)
```









