---
title: "E4 manuscript Results - Using ggplot"
author: "Marissa Lee"
date: "September 26, 2014"
output:
  pdf_document: default
  html_document: default
---
*Filename: e4_ms_results.Rmd'*

*A. This code needs the following files:*  

1. *'e4Data' folder*
  + 'e4_potData.txt'
  + 'e4_potData_dictionary.txt'
2. *'e4Code' folder*
  + 'e4_cleanCode.R'
  + 'e4_calcsiCode.R'
  + 'mytheme.R'
  + 'statFxns.R'
  + 'e4_Fig2stats.R' and 'e4_makeFig2.R' --> both reference --> 'e4_prepdfFig2.R'
  + 'e4_Fig3stats.R' and 'e4_makeFig3.R' --> both reference --> 'e4_prepdfFig3n4.R'
  + 'e4_Fig4stats.R' and 'e4_makeFig4.R' --> both reference --> 'e4_prepdfFig3n4.R'
  + 'e4_Fig5stats.R' and 'e4_makeFig5.R' --> both reference --> 'e4_prepdfFig5.R'

*B. This code does the following things:*  

1. Clean raw dataset (run external code)
2. *'e4Output_figures' folder* has Results section figures
    + Fig2. Species' biomass
    + Fig3. Soil measures vs Pot monoculture type
    + Fig4. Soil measures vs M.v. biomass w/o neighbors
    + Fig5. Soil measures vs M.v. biomass w/ neighbors, vs relative Mv abundance, vs total biomass
3. *'e4Output_tables' folder'* has txt tables that hold anova results and mean values



*C. R-related citations*
```{r,echo=TRUE, message=FALSE}
citation()
citation("lme4")
citation("lmerTest")
```



*******************

#1. Clean raw dataset (run external code)
```{r,echo=TRUE, message=FALSE}
source('e4Code/e4_cleanCode.R')
#str(data)

### Read-in all the custom functions for doing stats ###
source('e4Code/statFxns.R')
```

*******************

#2. Plot  




##Fig2 : Plant biomasses vs density trt  
```{r, echo=TRUE, warning=FALSE, message=FALSE, fig.height = 4, fig.width = 4}
source('e4Code/e4_Fig2stats.R')
source('e4Code/e4_makeFig2.R')
fig2 
```

###*e4Output_tables/fig2_means.txt* -- Figure 2 Means
```{r, echo=FALSE}
### Mean table
MEANS<-list(sum.fig2a.mivi, sum.fig2b)
meannames<-c('Mivi','Total')
i<-0
s.table<-numeric(0)
for (i in 1:length(MEANS)){
  s.tab<-PrettyMeans.2levs(MEANS[[i]])
  s.tab[,c('mean','se')]<-round(s.tab[,c('mean','se')], digits=2)
  lab<-rep(meannames[i], dim(s.tab)[1])
  sl.tab<-data.frame(lab, s.tab)
  
  s.table <- rbind(s.table, sl.tab)

}
colnames(s.table)[1:3]<-c('response','comptrt','mvtrt')
write.table(s.table, file='e4Output_tables/fig2_means.txt', sep='\t', row.names=F)
#s.table
```

###*e4Output_tables/fig2_lme_anova.txt* -- Microstegium biomass, relative abundance, and total plant biomass were shaped by the density treatment, neighbor treatment, and their interaction
```{r, echo=FALSE}
#lme4: y ~ mvtrt + comptrt + mvtrt:comptrt + (1|bk)

#Paste all anovas together
mivi<-lme.fig2a.mivi$anova
comp<-lme.fig2a.comp$anova
totalbiom<-lme.fig2b$anova
tmp<-rbind(mivi, comp,totalbiom)
resps.col<-rep(c('mivi', 'comp','totalbiom'), each=3)
terms.col<-rep(row.names(mivi), 3)
tmp2<-data.frame(resps.col,terms.col,tmp)
write.table(tmp2, file='e4Output_tables/fig2_lme_anova.txt', sep='\t', row.names=F)
#tmp2
```

###Microstegium biomass and relative abundance were X to X times lower in the presence of Sorghum than Panicum across density treatments (Fig 2)
```{r, echo=FALSE}

#Microstegium biomass
GreaterThan.fig2ab(PrettyMeans.2levs(sum.fig2a.mivi))
```

###Pots with Sorghum also had X to X times more total plant biomass than those given the Panicum neighbor treatment and X to X times more total plant biomass than the no neighbor treatment (Fig 2)
```{r, echo=FALSE}
#Total biomass
GreaterThan.fig2c(PrettyMeans.2levs(sum.fig2c))
```




##Fig3 : Monocultures vs total biomass and soil measurements
```{r, echo=TRUE, warning=FALSE, message=FALSE, fig.height=9, fig.width=3.5}
source('e4Code/e4_Fig3stats.R')
source('e4Code/e4_makeFig3.R')
fig3
```

###*e4Output_tables/fig3a_means.txt* -- Figure 3a Means
```{r, echo=FALSE}
### Mean table
s.tab<-PrettyMeans.2levs(sum.fig3.soil)
s.tab[,c('mean','se')]<-round(s.tab[,c('mean','se')], digits=2)

### Posthoc letters
# #nhdi
# PullTuks(lm.fig3.soil$tukys$nhdi) 
phl.nhdi<-c('a','ab','ab','b')

# #nodi
# PullTuks(lm.fig3.soil$tukys$nodi) 
phl.nodi<-c('a','b','bc','c')

# #toti
# PullTuks(lm.fig3.soil$tukys$totdi)
phl.totdi<-c('a','b','bc','c')

# #ammonifd
# PullTuks(lm.fig3.soil$tukys$ammonifd)
phl.ammonifd<-c('a','a','a','a')

# #nitrifd
# PullTuks(lm.fig3.soil$tukys$nitrifd)
phl.nitrifd<-c('a','a','a','a')

# #minzd
# PullTuks(lm.fig3.soil$tukys$minzd)
phl.minzd<-c('a','a','a','a')

# #soilmoi
# PullTuks(lm.fig3.soil$tukys$soilmoi)
phl.soilmoi<-c('a','a','a','b')

#all together
phl<-c(phl.nhdi, phl.nodi, phl.totdi, phl.ammonifd, phl.nitrifd, phl.minzd, phl.soilmoi)
table<-data.frame(s.tab,phl)
colnames(table)[1:2]<-c('soilmeas','type')
write.table(table, file='e4Output_tables/fig3a_means.txt', sep='\t', row.names=F)
```

###*e4Output_tables/fig3b_means.txt* -- Figure 3b Means
```{r,echo=FALSE}
### Mean table
s.tab<-sum.fig3.total
s.tab[,c('mean','se')]<-round(s.tab[,c('mean','se')], digits=2)

### Posthoc letters
# #total
# PullTuks(lm.fig3.total$tukys)
phl<-c('a','b','b','c')

table<-data.frame(s.tab,phl)
colnames(table)[1]<-c('type')
write.table(table, file='e4Output_tables/fig3b_means.txt', sep='\t', row.names=F)
```

###*e4Output_tables/fig3_lme_anova.txt* -- Soil measures and total biomass were shaped by the plant type  
```{r, echo=FALSE}
#lme4: y ~ type + (1|bk)

#soil measures
thing<-SoilUnlist(lme.fig3.soil)
tmp<-MakeTable(thing[['anovatab']])
#write.table(tmp, file='fig3_soil_lme_anova.txt', sep='\t', row.names=F)

#total biomass
thing1<-lme.fig3.total
#write.table(thing$anova, file='fig3_total_lme.txt', sep='\t', row.names=F)

#paste together anovas from soil measures and total biomass
tmp2<-data.frame('type','totalbiom',thing1$anova)
names(tmp2)<-names(tmp)
tmp3<-rbind(tmp,tmp2)
write.table(tmp3, file='e4Output_tables/fig3_lme_anova.txt', sep='\t', row.names=F)
```





##Fig4 : Mivi biomass vs soil measures w/o neighbors
```{r,echo=TRUE, warning=FALSE, message=FALSE, fig.height=9, fig.width=3.5}
source('e4Code/e4_Fig4stats.R')
source('e4Code/e4_makeFig4.R')
fig4.text
fig4.text.noempty
```

###*e4Output_tables/fig4_lme_anova.txt* and *e4Output_tables/fig4_lme_fe.txt* -- Soil measures varied by Mivi  
```{r, echo=FALSE}
#lme: resp <- mivi + I(mivi^2) + (1|bk)

#Includes empty pots
thing<-SoilUnlist(lme.fig4)
write.table(MakeTable(thing[['anovatab']]), file='e4Output_tables/fig4_lme_anova.txt', sep='\t', row.names=F)
write.table(MakeTable(thing[['fetab']]), file='e4Output_tables/fig4_lme_fe.txt', sep='\t', row.names=F)
f4anova<-MakeTable(thing[['anovatab']])
f4fe<-MakeTable(thing[['fetab']])

#Excludes empty pots
thing<-SoilUnlist(lme.fig4.noempty)
write.table(MakeTable(thing[['anovatab']]), file='e4Output_tables/fig4noempty_lme_anova.txt', sep='\t', row.names=F)
write.table(MakeTable(thing[['fetab']]), file='e4Output_tables/fig4noempty_lme_fe.txt', sep='\t', row.names=F)
f4anova.noe<-MakeTable(thing[['anovatab']])
f4fe.noe<-MakeTable(thing[['fetab']])

#compare nitrate
f4fe[f4fe$.id == 'nodi',]
f4fe.noe[f4fe.noe$.id == 'nodi',]

#compare totdi
f4fe[f4fe$.id == 'totdi',]
f4fe.noe[f4fe.noe$.id == 'totdi',]

```




##Fig5. Mixture plant biomass vs soil measures
+ Exclude pots without 2 species present
```{r,echo=FALSE}
#Calculate the change in soil measurement values in the presence of M.v. (run external code)
source('e4Code/e4_calcsiCode.R')
#str(datas)
```

```{r,echo=TRUE, warning=FALSE, message=FALSE,  fig.height=9, fig.width=4}
source('e4Code/e4_Fig5stats.R')
warnings()
source('e4Code/e4_makeFig5.R')
fig5
fig6


```

###*e4Output_tables/fig5_lme_mivi_anova.txt* and *e4Output_tables/fig5_lme_mivi_fe.txt* -- Soil measures varied by mivi and comptrt
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#lme: resp <- mivi + I(mivi^2) + comptrt + mivi:comptrt + (1|bk)
thing<-SoilUnlist(lme.fig5.mivi)
write.table(MakeTable(thing[['anovatab']]), file='e4Output_tables/fig5_lme_mivi_anova.txt', sep='\t', row.names=F)
write.table(MakeTable(thing[['fetab']]), file='e4Output_tables/fig5_lme_mivi_fe.txt', sep='\t', row.names=F)
```

###*e4Output_tables/fig5_lme_total_anova.txt* and *e4Output_tables/fig5_lme_total_fe.txt* -- Soil measures varied by total biomass  
```{r, echo=FALSE,warning=FALSE, message=FALSE}
#lme: resp <- relmivi + I(relmivi^2) + comptrt + relmivi:comptrt + (1|bk)
thing<-SoilUnlist(lme.fig6)
write.table(MakeTable(thing[['anovatab']]), file='e4Output_tables/fig6_lme_anova.txt', sep='\t', row.names=F)
write.table(MakeTable(thing[['fetab']]), file='e4Output_tables/fig6_lme_fe.txt', sep='\t', row.names=F)
```

###*e4Output_tables/fig5_means.txt* -- Mean soil measurement values by comptrt in mvtrt=1,2,4,5
```{r, echo=FALSE,warning=FALSE, message=FALSE}
### Mean table
s.tab<-PrettyMeans.2levs(sum.fig5.mivi)
s.tab[,c('mean','se')]<-round(s.tab[,c('mean','se')], digits=2)
write.table(s.tab, file='e4Output_tables/fig5_means.txt', sep='\t', row.names=F)
```

*******************

